---
title: "Super Soaker"
author: "Nelson, Yahui"
date: "2025-09-28"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading Super Soak Train data

```{r}
library(tidyverse)
library(tidymodels)
library(glmnet)
library(mice) #package for imputation
library(VIM) #visualizing missingness
library(naniar) #visualizing missingness
library(skimr) #alternative way to view dataset summaries
library(UpSetR) #visualizing missingness
library(readr)
train <- read_csv("train.csv")
knitr::opts_chunk$set(echo = FALSE)
```
Structure and summary
```{R}
str(train)
summary(train)
skim(train)
```

## Descriptive analysis of the Super Soaker data

```{r}
prop.table(table(train$failure))
```

There are 78.74% of the products pass the quality test, and 21.26% of the products failed the quality test.

### Visuals between failure variable and other variables

```{r}
train %>%
  ggplot(aes(x=loading))+
  geom_histogram(bins = 50,na_rm= TRUE,fill= "BLUE",alpha=0.7)+
  theme_minimal()+
  labs(title="Loading in Train Data")
```



```{r}
ggplot(train, aes(x=loading, na.rm= TRUE, fill = failure)) + geom_bar(width = 2) + theme_bw()+
  labs(title="Product absorption levels and whether the product failed the test")
```

The Failure rate are higher after 200ML absorption products


```{r}
ggplot(train, aes(x=attribute_0, fill = failure)) + geom_bar(width = 0.5) + theme_bw()+
  labs(title= "Product material 5 and 7 qulity test results")
```
The product uses material_7 are 4 times more than material_5, but the material_5's failure rate are slightly lower than material_7.


```{r}
ggplot(train, aes(x=attribute_1, fill = failure)) + geom_bar(width = 0.5) + theme_bw()+
  labs(title= "Product material 5,6 and 8 qulity test results")
```
Material_5 and material_8 are used more than material_6, but the failure rate are not too much different.


```{r}
ggplot(train, aes(x=product_code, fill = failure)) + geom_bar(width = 0.5) + theme_bw()+
  labs(title="Product prototype and qulity test result")
```
 
 Product_code with A through E's failure rate are not too much different.